Catchy Title Goes Here

### 2018-06-14 Paper/paper.tex
added new figures to paper

Figure~\ref{fig:foivhsimdata} shows the injected (dashed lines) and recovered (solid (purple or orange) lines) curves for the force of infection and vaccination hazard from simulated data with vaccine efficacy of $\gamma = 0.9$ (orange) and $\gamma = 0.6$ (indigo). The top panel shows the force of infection, and it is very clear from this panel that a Weibull distribution is not a good fit for the true force of infection, which is bimodal.  Because of this, we do not expect to be able to accurately infer the simulation parameters (i.e., $\gamma$). We examine the inferred values for this parameter in Figure~\ref{fig:veffsimdata}.

\begin{figure}
\includegraphics[width=\columnwidth,angle=0]{figures/foivhaz_fakedata_vaxserocase.pdf}
\caption{caption\label{fig:foivhsimdata}}
\end{figure}

\begin{figure}
\includegraphics[width=\columnwidth,angle=0]{figures/veff_fakedata.pdf}
\caption{caption\label{fig:veffsimdata}}
\end{figure}

@@

\begin{figure}
\includegraphics[width=\columnwidth,angle=0]{figures/vsc_simdata_vaxcase.pdf}
\caption{caption\label{fig:svcsimdata}}
\end{figure}

\subsection{DRC Data \label{subsec:DRC}}
Application to the DRC data
	Pairs plots for all provinces ? compare for fits with only case data to fits with case+serology ? discuss any appearance of non-identifiability (?? What is non-identifiability?)	
Figure 2 ? pairs plots for all provinces and two models

>>>>

Figure~\ref{fig:simplots} shows the injected (dashed lines) and recovered (solid (purple or orange) lines) curves for the force of infection and vaccination hazard from simulated data with vaccine efficacy of $\gamma = 0.9$ (orange) and $\gamma = 0.6$ (indigo). The top panel shows the force of infection, and it is very clear from this panel that a Weibull distribution is not a good fit for the true force of infection, which is bimodal.  Because of this, we do not expect to be able to accurately infer the simulation parameters (i.e., $\gamma$). We examine the inferred values for this parameter in Figure~\ref{fig:veffsimdata}.

\begin{figure*}
\includegraphics[width=\textwidth,angle=0]{figures/SimPlots-crop.pdf}
\caption{caption\label{fig:simplots}}
\end{figure*}

@@

\subsection{DRC Data \label{subsec:DRC}}
\begin{figure*}
\includegraphics[width=\textwidth,angle=0]{figures/VaccFOIveff-crop.pdf}
\caption{caption\label{fig:foivaccveff}}
\end{figure*}

\subsection{DRC Data \label{subsec:DRC}}
\begin{figure*}
\includegraphics[width=\textwidth,angle=0]{figures/SeroPlots-crop.pdf}
\caption{caption\label{fig:sero}}
\end{figure*}
Application to the DRC data
	Pairs plots for all provinces ? compare for fits with only case data to fits with case+serology ? discuss any appearance of non-identifiability (?? What is non-identifiability?)	
Figure 2 ? pairs plots for all provinces and two models
